%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt}
\newcommand{\CS}{C\#}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Joseph}{Schell}{ % Your name
{\bf JosephSchell510@gmail.com} | {\bf 510-965-3166} | {\bf Portland, OR}\\ % Your contact information
{\bf Falcon-Punch.github.io/Portfolio} % Your website, LinkedIn profile or other web address
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Pacific University}

\descript{Bachelor of Science\\Computer Science}
\location{Forest Grove, OR}
Expected Graduation May 2019\\
GPA: 3.57

\sectionspace % Some whitespace after the section

%------------------------------------------------


%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

GitHub: {\bf github.com/Falcon-Punch}\\
LinkedIn: {\bf www.linkedin.com/in/js510}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\descript{Proficient:}
C \textbullet{} C++ \textbullet{} Java \\
\descript{Experience with:}
\CS{} \textbullet{} Python \textbullet{} SQL \textbullet{} PHP \\
HTML5 \textbullet{} CSS \textbullet{} JavaScript \\
\descript{Technologies:}
Visual Studio \textbullet{} jQuery \textbullet{} Ajax \\
Android \textbullet{} UNIX / Linux \textbullet{} Valgrind \\
Unity \textbullet{} Git / GitHub \textbullet{} PowerShell \\
WordPress \textbullet{} Adobe Photoshop

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

Data Structures \\
Intro to Android Programming \\
Computer Security \\
Operating Systems \\
Discrete Math \\
Linear Algebra

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards} 
•  Math and CS Talent Award (Scholarship)\\
•  Pacific Scholarships in Math and Sciences Award (Scholarship)\\
•  Phi Theta Kappa Member Award (Scholarship)\\
•  Work Opportunity Tax Credit Eligible (For Potential Employers)\\
•  U.S. Navy Good Conduct Medal\\
•  Global War on Terrorism Service Medal\\
•  National Defense Service Ribbon

%\begin{tabular}{rll}
%2014	 & top 52/2500 & KPCB Engineering Fellow\\
%2014	 & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
%\end{tabular}

\sectionspace % Some whitespace after the section

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Music Site / Spotify Clone}
\hfill \descript{Aug 2018}

\location{Technologies used: HTML, CSS, PHP, MySQL, jQuery, Ajax}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item A music streaming website that allows the user to sign up for an account, search and store music into personalized playlists.
\item The site features an interactive music playing bar that allows the user to control the music via shuffle, repeat, play, pause, previous and next buttons.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Fractal Image Generator}
\hfill \descript{Aug 2018}

\location{Technologies used: C++, Visual Studio}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Draws pixels onto a bitmap image that forms recursive fractal designs using Mandelbrot’s algorithm.
\item The program also has a zoom function that allows the user to magnify images.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{UNIX Shell}
\hfill \descript{May 2018}

\location{Technologies used: C, Eclipse IDE, UNIX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Creation of a small command line interface in UNIX that utilizes child and parent processes.
\item Program includes input/output redirection, piping and background launching.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{UFO Flight School Video Game}
\hfill \descript{May 2018}

\location{Technologies used: \CS{}, Unity, PC Gaming}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Allows players to fly a UFO through six levels of mazes that grow increasingly more difficult.
\item Includes particle effects, moving obstacles, agile ship rotation and ship thrusting effects.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Silika Technologies}
\descript{Software Developer}

\location{June 2018 – Current | Hillsboro, OR}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Worked with senior consultants to help clients solve business needs.
\item Debugged and refactored code found in client software using Visual Studio.
\item Technologies worked with include: \CS{}, PowerShell, SQL, Git and Azure.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Intel Corporation}
\descript{Manufacturing Technician}

\location{Dec 2014 – May 2015 | Hillsboro, OR}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Completed tasks associated with all wafer and semiconductor production including equipment operations, engineering and training in a Class 1 clean room environment.
\item Communicated with the engineering department to test and resolve issues with product development.
\item Resolved nonstandard events within the product line to maintain continuity with operations.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------

\runsubsection{U.S. Navy}
\descript{Aviation Electrician}

\location{April 2008 – Nov 2015 | Lemoore, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Performed scheduled and unscheduled maintenance on electrical components for the F/A-18 naval aircraft in order to maintain crucial flight schedule operations.
\item Tested and troubleshot embedded electrical issues using schematics, oscilloscopes, ohmmeters, ammeters and voltmeters.
\item Collaborated with other electricians, technicians and engineers daily to apply group critical thinking methods to solve electrical aircraft issues.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}